\Large Taking uncertainty seriously \newline \normalsize A Bayesian approach to word embedding bias estimation

### 2022-03-01 presentations/presentationBoston/presentationBoston.tex

\title{\Large Taking uncertainty seriously \newline \normalsize A
Bayesian approach to word embedding bias estimation}
\author{Alicja Dobrzeniecka \& Rafal Urbaniak
\footnotesize \newline (LoPSE research group, University of Gdansk)}
\date{ExpSem2021, ESSLLI}

@@

\begin{itemize}
\item
  feminine occupations: ``homemaker,'' ``nurse,'' ``receptionist,''
  ``librarian,'' etc.
\item
  masculine occupations: ``maestro,'' ``captain,'' ``architect,''
  ``boss,'' etc.
\end{itemize}

@@

\begin{center}\includegraphics[width=0.6\linewidth]{presentationESSLLI_files/figure-beamer/unnamed-chunk-1-1} \end{center}
\normalsize
\end{block}
\end{frame}

@@

\begin{center}\includegraphics[width=0.55\linewidth]{presentationESSLLI_files/figure-beamer/unnamed-chunk-2-1} \end{center}
\normalsize

@@

\begin{center}\includegraphics[width=0.5\linewidth]{presentationESSLLI_files/figure-beamer/unnamed-chunk-3-1} \end{center}
\normalsize

@@

\begin{frame}{Some methodological problems}
\protect\hypertarget{some-methodological-problems-3}{}
\begin{block}{Distances for ``muslim''}
\protect\hypertarget{distances-for-muslim}{}
\begin{center}\includegraphics[width=0.8\linewidth]{presentationESSLLI_files/figure-beamer/unnamed-chunk-4-1} \end{center}
\end{block}
\end{frame}

\begin{frame}{Some methodological problems}
\protect\hypertarget{some-methodological-problems-4}{}
\begin{block}{Distances for ``priest''}
\protect\hypertarget{distances-for-priest}{}
\begin{center}\includegraphics[width=0.8\linewidth]{presentationESSLLI_files/figure-beamer/unnamed-chunk-5-1} \end{center}
\end{block}
\end{frame}

@@

\begin{center}\includegraphics[width=0.7\linewidth]{presentationESSLLI_files/figure-beamer/unnamed-chunk-6-1} \end{center}
\normalsize

@@

\begin{center}\includegraphics[width=0.8\linewidth]{presentationESSLLI_files/figure-beamer/unnamed-chunk-8-1} \end{center}
\normalsize
\end{block}
\end{frame}

@@

\begin{frame}{Bayesian model}
\protect\hypertarget{bayesian-model}{}
\begin{block}{Choosing priors}
\protect\hypertarget{choosing-priors}{}
\begin{center}\includegraphics[width=1\linewidth]{presentationESSLLI_files/figure-beamer/priorsVis-1} \end{center}
\end{block}
\end{frame}

@@

\begin{frame}{Dataset-level coefficients}
\protect\hypertarget{dataset-level-coefficients}{}
\begin{block}{Religion with 89\%-compatibility intervals (HPDI)}
\protect\hypertarget{religion-with-89-compatibility-intervals-hpdi}{}
\begin{center}
\begin{figure}[!htb]\centering
   \begin{minipage}{0.55\textwidth}
  \includegraphics[width=6cm]{../images/religionCoeffs.jpeg}
   \end{minipage} \begin{minipage}{0.4\textwidth}\footnotesize
   \begin{itemize}
   \item All HPDIs overlap with 0 
   \item Differences between classes are relatively small
   \item Coefficients for Race are similar
   \end{itemize}
   \end{minipage}
  \end{figure}

@@

\begin{frame}{Dataset-level coefficients}
\protect\hypertarget{dataset-level-coefficients-1}{}
\begin{block}{Gender with 89\%-compatibility intervals (HPDI)}
\protect\hypertarget{gender-with-89-compatibility-intervals-hpdi}{}
\begin{center}
\begin{figure}[!htb]\centering
  \begin{minipage}{0.55\textwidth}
\includegraphics[width=6cm]{../images/genderCoeffs.jpeg}
\end{minipage}
\begin{minipage}{0.4\textwidth}\footnotesize
   \begin{itemize}
   \item Associated and different are away from 0
   \item But they were supposed to be opposites and are very close to each other (co-occurrence?)
   \item Differences between classes are still relatively small
   \end{itemize}
   \end{minipage}
\end{figure}

@@

\begin{frame}{Word-level coefficients}
\protect\hypertarget{word-level-coefficients}{}
\begin{figure}[!htb]\centering
  \begin{minipage}{0.55\textwidth}
\includegraphics[width=7.5cm]{../images/visReligionReddit.png}
\end{minipage}
\begin{minipage}{0.4\textwidth}\footnotesize

@@

   \begin{itemize}
   \item Most intervals overlap with control groups
   \item Often not too much diffence between associated and different
   \end{itemize}
   \end{minipage}
\end{figure}
\end{frame}

\begin{frame}{Word-level coefficients}
\protect\hypertarget{word-level-coefficients-1}{}
\begin{figure}[!htb]\centering
  \begin{minipage}{0.55\textwidth}
\includegraphics[width=7.5cm]{../images/visGenderReddit.png}
\end{minipage}
\begin{minipage}{0.4\textwidth}\footnotesize

@@

\begin{frame}{Word-level coefficients}
\protect\hypertarget{word-level-coefficients-2}{}
\begin{figure}[!htb]\centering
  \begin{minipage}{0.55\textwidth}
\includegraphics[width=7.5cm]{../images/visRaceReddit.png}
\end{minipage}
\begin{minipage}{0.4\textwidth}\footnotesize

>>>>

\title{\Large Taking uncertainty seriously \newline \normalsize A
Bayesian approach to word embedding bias estimation}
\author{Alicja Dobrzeniecka \& Rafal Urbaniak
\footnotesize \newline (LoPSE research group, University of Gdansk)}
\date{Boston, April Fools' Day}

@@

\begin{itemize}
\item
  ``feminine'' occupations: ``homemaker,'' ``nurse,'' ``receptionist,''
  ``librarian,'' etc.
\item
  ``masculine'' occupations: ``maestro,'' ``captain,'' ``architect,''
  ``boss,'' etc.
\end{itemize}

@@

\begin{center}\includegraphics[width=0.6\linewidth]{presentationBoston_files/figure-beamer/unnamed-chunk-1-1} \end{center}
\normalsize
\end{block}
\end{frame}

@@

\begin{center}\includegraphics[width=0.55\linewidth]{presentationBoston_files/figure-beamer/unnamed-chunk-2-1} \end{center}
\normalsize

@@

\begin{center}\includegraphics[width=0.5\linewidth]{presentationBoston_files/figure-beamer/unnamed-chunk-3-1} \end{center}
\normalsize

@@

\begin{frame}{Some methodological problems}
\protect\hypertarget{some-methodological-problems-3}{}
\begin{block}{Distances for ``muslim''}
\protect\hypertarget{distances-for-muslim}{}
\begin{center}\includegraphics[width=0.8\linewidth]{presentationBoston_files/figure-beamer/unnamed-chunk-4-1} \end{center}
\end{block}
\end{frame}

\begin{frame}{Some methodological problems}
\protect\hypertarget{some-methodological-problems-4}{}
\begin{block}{Distances for ``priest''}
\protect\hypertarget{distances-for-priest}{}
\begin{center}\includegraphics[width=0.8\linewidth]{presentationBoston_files/figure-beamer/unnamed-chunk-5-1} \end{center}
\end{block}
\end{frame}

@@

\begin{center}\includegraphics[width=0.7\linewidth]{presentationBoston_files/figure-beamer/unnamed-chunk-6-1} \end{center}
\normalsize

@@

\begin{center}\includegraphics[width=0.8\linewidth]{presentationBoston_files/figure-beamer/unnamed-chunk-8-1} \end{center}
\normalsize
\end{block}
\end{frame}

@@

\begin{frame}{Bayesian model}
\protect\hypertarget{bayesian-model}{}
\begin{block}{Choosing priors}
\protect\hypertarget{choosing-priors}{}
\begin{center}\includegraphics[width=1\linewidth]{presentationBoston_files/figure-beamer/priorsVis-1} \end{center}
\end{block}
\end{frame}

@@

\begin{frame}{Dataset-level coefficients}
\protect\hypertarget{dataset-level-coefficients}{}
\begin{block}{Religion with 89\%-compatibility intervals (HPDI)}
\protect\hypertarget{religion-with-89-compatibility-intervals-hpdi}{}
\begin{center}
\begin{figure}[!htb]\centering
   \begin{minipage}{0.55\textwidth}
  \includegraphics[width=6cm]{../../images/religionCoeffs.jpeg}
   \end{minipage} \begin{minipage}{0.4\textwidth}\footnotesize
   \begin{itemize}
   \item All HPDIs overlap with 0 
   \item Differences between classes are relatively small
   \item Coefficients for Race are similar
   \end{itemize}
   \end{minipage}
  \end{figure}

@@

\begin{frame}{Dataset-level coefficients}
\protect\hypertarget{dataset-level-coefficients-1}{}
\begin{block}{Gender with 89\%-compatibility intervals (HPDI)}
\protect\hypertarget{gender-with-89-compatibility-intervals-hpdi}{}
\begin{center}
\begin{figure}[!htb]\centering
  \begin{minipage}{0.55\textwidth}
\includegraphics[width=6cm]{../../images/genderCoeffs.jpeg}
\end{minipage}
\begin{minipage}{0.4\textwidth}\footnotesize
   \begin{itemize}
   \item Associated and different are away from 0
   \item But they were supposed to be opposites and are very close to each other (co-occurrence?)
   \item Differences between classes are still relatively small
   \end{itemize}
   \end{minipage}
\end{figure}

@@

\begin{frame}{Word-level coefficients}
\protect\hypertarget{word-level-coefficients}{}
\begin{figure}[!htb]\centering
  \begin{minipage}{0.55\textwidth}
\includegraphics[width=7.5cm]{../../images/visReligionReddit.png}
\end{minipage}
\begin{minipage}{0.4\textwidth}\footnotesize

@@

   \begin{itemize}
   \item Most intervals overlap with control groups
   \item Often not too much difference between associated and different
   \end{itemize}
   \end{minipage}
\end{figure}
\end{frame}

\begin{frame}{Word-level coefficients}
\protect\hypertarget{word-level-coefficients-1}{}
\begin{figure}[!htb]\centering
  \begin{minipage}{0.55\textwidth}
\includegraphics[width=7.5cm]{../../images/visGenderReddit.png}
\end{minipage}
\begin{minipage}{0.4\textwidth}\footnotesize

@@

\begin{frame}{Word-level coefficients}
\protect\hypertarget{word-level-coefficients-2}{}
\begin{figure}[!htb]\centering
  \begin{minipage}{0.55\textwidth}
\includegraphics[width=7.5cm]{../../images/visRaceReddit.png}
\end{minipage}
\begin{minipage}{0.4\textwidth}\footnotesize
